\tool

### 2018-04-03 paper/paper.tex
Reading group abstract and intro changes

\begin{abstract}
To increase software user productivity, toolsmiths create tools and features to automatically complete software tasks. However, these useful tools are often undiscovered or ignored by users, which can be problematic for industries that rely on worker efficiency and correctness, such as software engineering. This paper introduces \tool, a novel automated recommendation system developed for researchers to make recommendations and increase awareness of their products. To help improve tool adoption among software engineers, \tool~integrates concepts from peer interactions and software engineering industry practices to suggest tools to developers, and our results suggest that this approach is effective in making tool recommendations to software developers on GitHub repositories.
\end{abstract}
\keywords{Software Engineering; Tool Recommendations; Tool Discovery;}

@@

Software is increasingly prevalent in our society. To keep up with rising demands for new technology, software engineers are making efforts to emphasize \textit{software quality}. Throughout the software development life cycle, companies focus on metrics that impact both software producers and consumers such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}. However, despite increased attention to improving software quality, buggy code remains a persisting and escalating problem.

The Software Fail Watch by Tricentis discovered that software failures impacted approximaltely half of the world's population (3.7 billion users) and caused \$1.7 trillion in financial losses in 2017.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs in code, or debugging, is becoming increasingly time-consuming and costly.  A study by the National Institute of Standards and Technology reported that software engineers spend 70-80\% of their time debugging at work, and one error takes an average of 17.4 hours to debug~\cite{NIST}. Studies also show the cost of fixing an error becomes more expensive the longer it exists in source code~\cite{SEEconomics, SoftwareAssuranceSDLC}.

To improve code quality and prevent errors, researchers and toolsmiths have created software engineering tools to aid developers in their work. These tools automatically perform a wide variety of software development tasks to save time and effort for programmers. The Software Engineering Body of Knowledge indicates the importance of development tools used to achieve ``desirable characteristics of software products'', noting they are part of defining software quality~\cite{SWEBOK}. Research shows tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, navigation, and more are useful for enhancing code. Ultimately, utilizing software enginering tools can lead to reduced debugging costs and increased developer productivity.

Althouth quality is a primary concern for software engineers and users, developers rarely use tools designed to improve quality~\cite{Johnson2013Why}. There are many barriers to tool adoption, and one of the primary reasons useful tools are underused or ignored is the discoverability barrier, or when users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of awareness for software engineering tools can lead to poor code quality, harmed users, and significant amounts of time and money spent fixing errors. While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that learning about tools from colleagues during normal work activities, or \textit{peer interaction}, is the most effective mode of tool discovery~\cite{MurphyHill2011PeerInteraction}.

To help solve the tool discovery problem among software engineers, we developed \tool. Our system automatically recommends development tools by integrating characteristics of peer interactions and software engineering practices. \tool~is designed for toolsmiths to increase awareness of their products by systematically running their tools and making customized recommendations to developers on GitHub\footnote{https://github.com}, the largest code hosting platform in the world~\cite{GousiosGitHub}. This paper seeks to answer the following research questions (RQs): \\

@@

To answer these questions, we evaluated \tool~with \textsc{Error Prone}\footnote{http://errorprone.info}, an open source Java static analysis tool. We examined the frequency of recommendations and how developers reacted to receiving suggestions from our system. This research makes the following contributions:

>>>>

\begin{abstract}
To increase software user productivity, toolsmiths create tools and features to automatically complete software tasks. However, these useful tools are often undiscovered or ignored by potential users, which can be problematic for industries, such as software engineering, that rely on worker efficiency and correctness. This paper introduces \tool, a novel automated recommendation system developed for researchers to make recommendations and increase awareness of their products. To help improve tool adoption among software engineers, \tool~integrates concepts from peer interactions and software engineering industry practices to suggest tools to developers, and our results suggest that this approach is effective in making tool recommendations to software developers on GitHub repositories.
\end{abstract}
\keywords{Software Engineering; Tool Recommendations; Tool Discovery;}

@@

Software is becoming increasingly prevalent in our society. To keep up with rising demands for new technology, software engineers are making efforts to emphasize \textit{software quality}. Throughout the software development life cycle, companies focus on metrics that impact both software producers and consumers such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}. However, despite increased attention to improving software quality, buggy code remains a persisting and escalating problem.

The 2017 Software Fail Watch by Tricentis discovered that software failures affected approximaltely half of the world's population impacting 3.7 billion users, and caused \$1.7 trillion in financial losses.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs in code, or debugging, continues to become increasingly time-consuming and costly.  A study by the National Institute of Standards and Technology reported that software engineers spend 70-80\% of their time debugging at work, and one error takes an average of 17.4 hours to debug~\cite{NIST}. Studies also show the cost of fixing an error becomes more expensive the longer it exists in source code~\cite{SEEconomics, SoftwareAssuranceSDLC}.

To improve code quality and prevent errors, researchers and toolsmiths have created software engineering tools to aid developers in their work. Prior work shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, and more are beneficial for improving code. These tools automatically perform a wide variety of software development tasks to save time and effort for developers. Additionally, the Software Engineering Body of Knowledge indicates the importance of development tools, noting they can be used to achieve ``desirable characteristics of software products''~\cite{SWEBOK}. Utilizing software enginering tools can reduce software errors and debugging costs while increasing developer productivity.

Althouth quality is a primary concern for developers and users and many software engineering tools exist to help improve code and prevent bugs, developers rarely use these tools~\cite{Johnson2013Why}. One of the primary barriers to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of awareness for software engineering tools can lead to poor code quality, inconvenienced users, and significant amounts of time and money spent fixing errors. While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that learning about tools from colleagues during normal work activities, or \textit{peer interaction}, is the most effective mode of tool discovery~\cite{MurphyHill2011PeerInteraction}.

To help solve the tool discovery problem among software engineers, we developed \tool. Our system automatically recommends development tools by analyzing developer changes and integrating characteristics of peer interactions and software engineering practices. \tool~is designed for toolsmiths to increase awareness of their products by systematically running their tools and making customized recommendations to developers on GitHub\footnote{https://github.com}, the largest code hosting platform in the world~\cite{GousiosGitHub}. This paper seeks to answer the following research questions (RQs): \\

@@

To answer these questions, we evaluated \tool~recommending \textsc{Error Prone}\footnote{http://errorprone.info}, an open source Java static analysis tool. We examined the frequency of recommendations and how developers reacted to receiving suggestions from our system. This research makes the following contributions:
